---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

# awsathena

rJava Interface to AWS Athena SDK

## Description

Provides R wrapper methods to core 'aws-java-sdk-athena' Java library methods
to interrogate and orchestrate Amazon Athena queries.

## What's Inside the Tin?

The following functions are implemented:

- `collect_async`:	Collect Amazon Athena 'dplyr' query results asynchronously
- `download_query_execution_results`:	Use S3 to download the results of an Athena Query
- `get_query_execution`:	Get Query Execution
- `list_query_executions`:	List Query Executions
- `s3_download_file`:	Download a key from a bucket to a local file
- `start_query_execution`:	Start Query Execution
- `stop_query_execution`:	Stop Query Execution

## Installation

```{r eval=FALSE}
devtools::install_git("git@git.sr.ht:~hrbrmstr/awsathena")
# OR
devtools::install_gitlab("hrbrmstr/awsathena")
# OR
devtools::install_github("hrbrmstr/awsathena")
```

## Usage

```{r}
library(rJava)
library(awsathenajars)
library(awsathena)

packageVersion("awsathena")
```

### Basics

```{r}
qx <- list_query_executions(profile = "personal")

head(qx)

str(get_query_execution(qx[[1]], profile = "personal"), 1)
```

## `awsathenajars` Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

